\textbf{NBA Party}

### 2017-07-05 init_model.rnw
Now using a density overlay on histogram of season-teams meet the spread plot.

stargazer(mp, covariate.labels = c('party placebo', 'lag changes in posession', 'logged travel distance', 'east-west travel direction', 'number hours rest time', 'time of game during day', 'home team effect', 'logged travel distance * east-west', 'Constant'),
          dep.var.labels = 'Meet the Spread (NBA)')

@@

### Meet the spread for both NBA and MLB
pdf('writing/meet_the_spread.pdf')
par(mfcol = c(2, 1))
nba.lines[, list(meet.spread = mean(outcome == 'W')), 
          by = list(season, team)][, hist(meet.spread, 
                                          main = paste('How often do teams meet the spread? (NBA)', 
                                                       'By season-team, 2010-11 through 2016-17',
                                                       sep = '\n'),
                                          xlab = 'Meet the Spread', breaks = 25)]
### There should be 'no information' left over after conditioning on odds.
noinf <- lm(I(team.score > opponent.score) ~ odds, data = mlb.lines)
preds <- fitted(noinf)
mlb.lines[, fitted := fitted(noinf)]
mlb.lines[, resid  := resid(noinf)]
mlb.lines[, list(avg.residual = mean(resid)), by = round(fitted, 3)] %>% 
    plot(., xlab = 'Fitted Probability', ylab = 'Average Residual', 
         main = paste('After conditioning on bookkeeper\'s odds (MLB),',
                      'successful prediction is a coin-flip', sep = '\n'))
abline(a = 0, b = 0, col = 'red', lty = 'dashed')
dev.off()

>>>>

stargazer(mp, covariate.labels = c('Party placebo', 'Lag changes in posession', 
                                   'Logged travel distance', 'East-west travel direction', 
                                   'Number hours rest time', 'Time of game during day', 
                                   'Home team effect', 'Logged travel distance * east-west', 
                                   'Constant'),
          dep.var.labels = 'Meet the Spread (NBA)')

@@

### Meet the spread for both NBA and MLB
pdf('writing/meet_the_spread.pdf')
par(mfcol = c(2, 1))
tmp <- nba.lines[, list(meet.spread = mean(outcome == 'W')), 
          by = list(season, team)]
hist(tmp$meet.spread, prob = T, main = paste('How often do teams meet the spread? (NBA)', 
                                             'By season-team, 2010-11 through 2016-17',
                                             sep = '\n'),
     xlab = 'Meet the Spread', breaks = 25)
lines(density(tmp$meet.spread, adjust = 2), col = 'orange', lty = 'dashed')
### There should be 'no information' left over after conditioning on odds.
noinf <- lm(I(team.score > opponent.score) ~ odds, data = mlb.lines)
preds <- fitted(noinf)
mlb.lines[, fitted := fitted(noinf)]
mlb.lines[, resid  := resid(noinf)]
mlb.lines[, list(avg.residual = mean(resid)), by = round(fitted, 3)] %>% 
    plot(., xlab = 'Fitted Probability', ylab = 'Average Residual', 
         main = paste('After conditioning on bookkeeper\'s odds (MLB),',
                      'successful prediction is a coin-flip', sep = '\n'))
abline(a = 0, b = 0, col = 'orange', lty = 'dashed')
dev.off()
